Time Is Running Out

### 2023-05-21 abstract.tex
Verbeteringen pa

In a society where social media is so ubiquitous present, the privacy concerns
around them are more relevant than ever. While developing applications, privacy
laws and concerns must be taken into account. But this does not mean all these
platforms that where built whit those in mind are bulletproof. In a lot of
applications it is still possible to find vulnerabilities in the system, with
the possibility of rather unpleasant consequences. During this thesis, the main
focus will be on the privacy policies of fitness trackers. Fitness trackers are
platforms which store and display data related to sport activities. These can
be shared with other users, to show your achievements, and possibly motivating
others to exercise as well. This data may include heart rate, GPS-locations,
etc. Some pieces could potentially be more privacy-sensitive than others. The
relevant data to study in this thesis are GPS-locations and GPS-related data
(like speed, distance, \ldots). A great concern about sharing GPS-data, is
potentially sharing locations you would rather keep private, for example your
home location. Sharing full GPS data of your activities could leak this
location.

>>>>

In a society where social media is so ubiquitous, the privacy concerns around
them are more relevant than ever. While developing applications, privacy laws
and concerns must be taken into account. But this does not mean all these
platforms that where built whit those in mind are bulletproof. In a lot of
applications it is still possible to find vulnerabilities in the system, with
the possibility of rather unpleasant consequences. During this thesis, the main
focus will be on the privacy policies of fitness trackers. Fitness trackers are
platforms which store and display data related to sport activities. These can
be shared with other users, to show your achievements, and possibly motivating
others to exercise as well. This data may include heart rate, GPS-locations,
etc. Some pieces could potentially be more privacy-sensitive than others. The
relevant data to study in this thesis are GPS-locNations and GPS-related data
(like speed, distance, \ldots). A great concern about sharing GPS-data, is
potentially sharing locations you would rather keep private, for example your
home location. Sharing full GPS data of your activities could leak this
location.

### 2023-05-21 article.tex
DBSCAN & Entry Gates
Verbeteringen pa

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
should not be used}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
    \and
    \IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
    \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
        \textit{name of organization (of Aff.)}\\
        City, Country \\
        email address or ORCID}
}

\maketitle

\begin{abstract}
    This document is a model and instructions for \LaTeX.
    This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes,
    or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
    component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX. Please observe the
conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All
margins, column widths, line spaces, and text fonts are prescribed; please do
not alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement and others
are deliberate, using specifications that anticipate your paper as one part of
the entire proceedings, and not as an independent document. Please do not
revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a
separate text file. Complete all content and organizational editing before
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information
on proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been
formatted and styled. Do not number text heads---{\LaTeX} will do that for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text,
even after they have been defined in the abstract. Abbreviations such as IEEE,
SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use
abbreviations in the title or heads unless they are unavoidable. ~
\subsection{Units}
\begin{itemize}
    \item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English
          units may be used as secondary units (in parentheses). An exception would be
          the use of English units as identifiers in trade, such as ``3.5-inch disk
          drive''.
    \item Avoid combining SI and CGS units, such as current in amperes and magnetic field
          in oersteds. This often leads to confusion because equations do not balance
          dimensionally. If you must use mixed units, clearly state the units for each
          quantity that you use in an equation.
    \item Do not mix complete spellings and abbreviations of units:
          ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not
          ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``.
          . . a few henries'', not ``. . . a few H''.
    \item Use a zero before decimal points: ``0.25'', not ``.25''. Use
          ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your equations more compact, you may
use the solidus (~/~), the exp function, or appropriate exponents. Italicize
Roman symbols for quantities and variables, but not Greek symbols. Use a long
dash rather than a hyphen for a minus sign. Punctuate equations with commas or
periods when they are part of a sentence, as in:
\begin{equation}
    a+b=\gamma\label{eq}
\end{equation}

Be sure that the symbols in your equation have been defined before or
immediately following the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}''
or ``equation \eqref{eq}'', except at the beginning of a sentence: ``Equation
\eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead of
``hard'' references (e.g., \verb|(1)|). That will make it possible to combine
sections, add equations, or change the order of figures or citations without
having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use \verb|{align}|
or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}| environment leaves
unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX} will
increment the main equation counter even when there are no equation numbers
displayed. If you forget that, you might write an article in which the equation
numbers skip from (17) to (20), causing the copy editors to wonder if you've
discovered a new method of counting.

    {\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

    {\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It will not
stop equation numbers inside \verb|{array}| (there won't be any anyway) and it
might stop a wanted equation number in the surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
    \item The word ``data'' is plural, not singular.
    \item The subscript for the permeability of vacuum $\mu_{0}$, and other common
          scientific constants, is zero with subscript formatting, not a lowercase letter
          ``o''.
    \item In American English, commas, semicolons, periods, question and exclamation
          marks are located within quotation marks only when a complete thought or name
          is cited, such as a title or full quotation. When quotation marks are used,
          instead of a bold or italic typeface, to highlight a word or phrase,
          punctuation should appear outside of the quotation marks. A parenthetical
          phrase or statement at the end of a sentence is punctuated outside of the
          closing parenthesis (like this). (A parenthetical sentence is punctuated within
          the parentheses.)
    \item A graph within a graph is an ``inset'', not an ``insert''. The word
          alternatively is preferred to the word ``alternately'' (unless you really mean
          something that alternates).
    \item Do not use the word ``essentially'' to mean ``approximately'' or
          ``effectively''.
    \item In your paper title, if the words ``that uses'' can accurately replace the word
          ``using'', capitalize the ``u''; if not, keep using lower-cased.
    \item Be aware of the different meanings of the homophones ``affect'' and ``effect'',
          ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal''
          and ``principle''.
    \item Do not confuse ``imply'' and ``infer''.
    \item The prefix ``non'' is not a word; it should be joined to the word it modifies,
          usually without a hyphen.
    \item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
    \item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.''
          means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A
minimum of one author is required for all conference articles. Author names
should be listed starting from left to right and then moving down to the
next line. This is the author sequence that will be used in future citations
and by indexing services. Names should not be listed in columns nor group by
affiliation. Please keep your affiliations as succinct as possible (for
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not
topically subordinate to each other. Examples include Acknowledgments and
References and, for these, the correct style to use is ``Heading 5''. Use
``figure caption'' for your Figure captions, and ``table head'' for your table
title. Run-in heads, such as ``Abstract'', will require you to apply a style
(in this case, italic) in addition to the style provided by the drop down menu
to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For
example, the paper title is the primary text head because all subsequent
material relates and elaborates on this one topic. If there are two or more
sub-topics, the next level head (uppercase Roman numerals) should be used and,
conversely, if there are not at least two sub-topics, then no subheads should
be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and bottom of columns. Avoid placing them
in the middle of columns. Large figures and tables may span across both
columns. Figure captions should be below the figures; table heads should appear
above the tables. Insert figures and tables after they are cited in the text.
Use the abbreviation ``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
    \caption{Table Type Styles}
    \begin{center}
        \begin{tabular}{|c|c|c|c|}
            \hline
            \textbf{Table} & \multicolumn{3}{|c|}{\textbf{Table Column Head}}                                                         \\
            \cline{2-4}
            \textbf{Head}  & \textbf{\textit{Table column subhead}}           & \textbf{\textit{Subhead}} & \textbf{\textit{Subhead}} \\
            \hline
            copy           & More table copy$^{\mathrm{a}}$                   &                           &                           \\
            \hline
            \multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
        \end{tabular}
        \label{tab1}
    \end{center}
\end{table}

\begin{figure}[htbp]
    \centerline{\includegraphics{fig/image.jpg}}
    \caption{Example of a figure caption.}
    \label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words rather
than symbols or abbreviations when writing Figure axis labels to avoid
confusing the reader. As an example, write the quantity ``Magnetization'', or
``Magnetization, M'', not just ``M''. If including units in the label, present
them within parentheses. Do not label axes only with units. In the example,
write ``Magnetization (A/m)'' or ``Magnetization \{A[m(1)]\}'', not just
``A/m''. Do not label axes with a ratio of quantities and units. For example,
write ``Temperature (K)'', not ``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without an
``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. G.)
thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The sentence
punctuation follows the bracket \cite{b2}. Refer simply to the reference
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference
\cite{b3}'' except at the beginning of a sentence: ``Reference \cite{b3} was
the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at the
bottom of the column in which it was cited. Do not put footnotes in the
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use ``et
al.''. Papers that have not been published, even if they have been submitted
for publication, should be cited as ``unpublished'' \cite{b4}. Papers that have
been accepted for publication should be cited as ``in press'' \cite{b5}.
Capitalize only the first word in a paper title, except for proper nouns and
element symbols.

For papers published in translation journals, please give the English citation
first, followed by the original foreign-language citation
\cite{PhilipsAndParks}.

\bibliographystyle{IEEEtran}
\bibliography{bibliografie}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts{}
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%lijst van afkortingen toevoegen?

% \setlength{\parskip}{8pt}
\begin{document}

\title{\textbf{\LARGE Time Is Running Out\\
        \large Assessing Temporal Privacy of Privacy Zones in Fitness Tracking Social Networks}
}

\author{
    \IEEEauthorblockN{Deleu, Wout}
    \IEEEauthorblockA{
        \textit{KU Leuven, Campus Rabot} \\
        Ghent, Belgium
    }
}
\maketitle

\begin{abstract}
    In a society where social media is so ubiquitous, the privacy concerns
    around them are more relevant than ever.  During this article, the main
    focus will be on the privacy policies of fitness trackers. Fitness trackers are
    platforms which store and display data related to sport activities. These can
    be shared with other users. This data may include heart rate, GPS-locations,
    etc. This type of data sharing can however cause unintentionally sharing of
    sensitive information, like home addresses.

    Most fitness tracking networks are aware of this danger and implement a series
    of countermeasures to prevent this. One of these countermeasures is the use of
    Endpoint Privacy Zones (EPZs) which is a zone around a sensitive location,
    which hides the part of the trajectory which ends or begins in this zone.
    Previous research has shown that it is possible to retrieve the sensitive
    location using the available data from the activity. Dhondt et al.\ showed that
    based on the total distance travelled, the sensitive location can be retrieved
    using an `inference attack'~\cite{Dhondt}. This study will investigate the
    possibilities of such inference attacks using other data than the distance. We
    want to recreate the results as good as possible using the speed and tempo of
    the activity, together with GPS-locations. This can result in an attack model
    with a success rate up to 75\%. This is lower than the previous implementation
    of Dhondt et al., but this shows that the attack is still possible under
    circumstances where the distance is rendered unusable. This also includes some
    countermeasure described by Dhondt et al. But countermeasures like enlarging
    the EPZ or shifting endpoints still have effect.\vspace{10pt}

    \textbf{Keywords}: fitness-trackers, privacy, gps-locations, endpoint privacy
    zone, inference attack
\end{abstract}

\section{Introduction}

\bibliographystyle{IEEEtran}
\bibliography{bibliografie_eng}
\end{document}

### 2023-05-21 hfdst4.tex
Verbeteringen pa

Allereerst bestuderen we de aanwezigheid van \ac{gps}-fouten in de vorm van
signal losses of pauzes. Dit gebeurt door de afstand tussen twee opeenvolgende
\ac{gps}-punten te bestuderen.
Tabel~\ref{tab:distance_between_gps_points_table} geeft een globaal overzicht
van deze verdeling, en de volledige verdeling is terug te vinden op
Figuur~\ref{fig:distance_between_gps_points_CDF}. De gemiddelde afstand tussen
twee opeenvolgende locaties is $6.41m$, met een standaardafwijking van
$42.53m$. Het gemiddelde is relatief laag, wat kan wijzen op accurate gegevens,
maar de hoge standaardafwijking wijst op grote schommelingen. Op de grafiek en
in de tabel is te zien dat de meeste afstanden onder de $20m$ liggen, wat
opnieuw een indicatie kan zijn van een degelijke precisie. Er is echter wel een
klein deel van de \ac{gps}-punten die een grote onderlinge afstanden vertoond.
Door de omvang van het aantal \ac{gps}-punten, en een gemiddeld aantal punten
per activiteit van $2574.90$, valt dit zeker niet te verwaarlozen. Als we
empirisch stellen dat een significant verschil $50$ meter bedraagt, dan ligt
0.9\% van de data boven deze drempel. Per activiteit zou dit dan resulteren op
gemiddeld $23$ afwijkende punten, wat zeker kan zorgen voor een significante
afwijking op de resulterende afstand.
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
        \toprule
        \midrule
        Total number of gps-points                    & $1.070 \cdot 10^8$       \\
        \hline
        distance between 2 gps points 20m $>$ 10m     & $13.91\%$                \\
        distance between 2 gps points 75m $>$ 50m     & $8.80 \cdot 10^{-1}\%$   \\
        distance between 2 gps points 100m $>$ 75m    & $9.11 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 150m $>$ 100m   & $4.99 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 200m $>$ 150m   & $1.97 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 500m $>$ 200m   & $3.47 \cdot  10^{-3} \%$ \\
        distance between 2 gps points 1000m $>$ 500m  & $1.26 \cdot 10^{-3} \%$  \\
        distance between 2 gps points 2000m $>$ 1000m & $9.39 \cdot 10^{-4}$ \%  \\
        distance between 2 gps points $>$ 2000m       & $4.056 \cdot 10^{-4} \%$ \\
        \midrule
        \bottomrule
    \end{tabular}
    \captionsetup{justification=centering}
    \caption{Verdeling van de afstanden tussen twee opeenvolgende gps-punten}\label{tab:distance_between_gps_points_table}
\end{table}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{fig/Afwijkingen&Analyses/Graphs/Afstand tussen 2 gps-punten.png}
    \caption{Verdeling van de afstanden tussen twee opeenvolgende gps-punten}\label{fig:distance_between_gps_points_CDF}
\end{figure}

>>>>

Allereerst bestuderen we de aanwezigheid van \ac{gps}-fouten in de vorm van
signal losses of pauzes. Dit gebeurt door de afstand tussen twee opeenvolgende
\ac{gps}-punten te bestuderen.
Tabel~\ref{tab:distance_between_gps_points_table} geeft een globaal overzicht
van deze verdeling, en de volledige verdeling is terug te vinden op
Figuur~\ref{fig:distance_between_gps_points_CDF}. De gemiddelde afstand tussen
twee opeenvolgende locaties is $6.41$ meter, met een standaardafwijking van
$42.53$ meter. Het gemiddelde is relatief laag, wat kan wijzen op accurate
gegevens, maar de hoge standaardafwijking wijst op grote schommelingen. Op de
grafiek en in de tabel is te zien dat de meeste afstanden onder de $20$ meter
liggen, wat opnieuw een indicatie kan zijn van een degelijke precisie. Er is
echter wel een klein deel van de \ac{gps}-punten die een grote onderlinge
afstanden vertoond. Door de omvang van het aantal \ac{gps}-punten, en een
gemiddeld aantal punten per activiteit van $2574.90$, valt dit zeker niet te
verwaarlozen. Als we empirisch stellen dat een significant verschil $50$ meter
bedraagt, dan ligt 0.9\% van de data boven deze drempel. Per activiteit zou dit
dan resulteren op gemiddeld $23$ afwijkende punten, wat zeker kan zorgen voor
een significante afwijking op de resulterende afstand.
\begin{table}[h]
    \centering
    \begin{tabular}{lr}
        \toprule
        \midrule
        Total number of gps-points                    & $1.070 \cdot 10^8$       \\
        \hline
        distance between 2 gps points 20m $>$ 10m     & $13.91\%$                \\
        distance between 2 gps points 75m $>$ 50m     & $8.80 \cdot 10^{-1}\%$   \\
        distance between 2 gps points 100m $>$ 75m    & $9.11 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 150m $>$ 100m   & $4.99 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 200m $>$ 150m   & $1.97 \cdot 10^{-3}\%$   \\
        distance between 2 gps points 500m $>$ 200m   & $3.47 \cdot  10^{-3} \%$ \\
        distance between 2 gps points 1000m $>$ 500m  & $1.26 \cdot 10^{-3} \%$  \\
        distance between 2 gps points 2000m $>$ 1000m & $9.39 \cdot 10^{-4}$ \%  \\
        distance between 2 gps points $>$ 2000m       & $4.056 \cdot 10^{-4} \%$ \\
        \midrule
        \bottomrule
    \end{tabular}
    \captionsetup{justification=centering}
    \caption{Verdeling van de afstanden tussen twee opeenvolgende gps-punten}\label{tab:distance_between_gps_points_table}
\end{table}
\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{fig/Afwijkingen&Analyses/Graphs/Afstand tussen 2 gps-punten.png}
    \caption{Verdeling van de afstanden tussen twee opeenvolgende gps-punten}\label{fig:distance_between_gps_points_CDF}
\end{figure}
